Co-evolution of lexical meaning \& pragmatic use

### 2018-03-17 paper/cogsci-submission2.tex
minor fixes first sections

We consider three types and three possible data observations they can produce. Types are
equally likely \emph{a priori}, but show different and crucially asymmetric production
behavior. The likelihood with which type $t_i$ produces datum $d_j$ is $LH_{ij}$:
\begin{align*}
  LH & = \begin{blockarray}{lccc}
    & d_1 & d_2 & d_3 \\
    \begin{block}{l[ccc]}
      t_1 & 1-2\epsilon & \epsilon & \epsilon \\
      t_2 & \delta & 1-(\epsilon + \delta) & \epsilon \\
      t_2 & \delta & \epsilon & 1-(\epsilon + \delta)  \\
    \end{block}
  \end{blockarray}
\end{align*}
If $\delta > \epsilon$, production likelihoods are asymmetrically skewed to possibly favor
$t_1$, in the sense that both types $t_2$ and $t_3$  produce behavior that is strong
evidence for $t_1$ more often than behavior that is strong evidence for any other
type other then themselves. Type $t_1$ makes no such ``asymmetric mistakes''.

>>>>

We consider three types and three possible data observations they can produce. Types are
equally likely \emph{a priori}, but show different and crucially asymmetric production
behavior. The likelihood with which type $t_i$ produces datum $d_j$ is $LH_{ij}$:
\begin{align*}
  LH & = \begin{blockarray}{lccc}
    & d_1 & d_2 & d_3 \\
    \begin{block}{l[ccc]}
      t_1 & 1-2\epsilon & \epsilon & \epsilon \\
      t_2 & \delta & 1-(\epsilon + \delta) & \epsilon \\
      t_2 & \delta & \epsilon & 1-(\epsilon + \delta)  \\
    \end{block}
  \end{blockarray}
\end{align*}
If $\delta > \epsilon$, production likelihoods are asymmetrically skewed to favor $t_1$, in the
sense that both types $t_2$ and $t_3$ produce behavior that is strong evidence for $t_1$ more
often than behavior that is strong evidence for any other type different from themselves. Type
$t_1$ makes no such ``asymmetric mistakes'' and is more faithfully recognized based on its
production behavior than the other types.
